---
title: "Data 607 Assignment 9"
author: "Mohamed Hassan-El Serafi"
date: "2023-03-26"
output: html_document
---



Using an API key for The New York Times, I retrieved data of most viewed articles on NYTimes.com in the past 30 days: 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=F, warnings=F)
```


```{r}
library(tidyverse)
library(RCurl)
library(rjson)
library(DT)
library(data.table)
library(httr)
library(kableExtra)
```





#### Storing API link 

```{r}
nyt_json_url <- "https://api.nytimes.com/svc/mostpopular/v2/viewed/30.json?api-key=BG3ZhQtYKZ7YG8bmO5ei49K4qG1mHYQh"
```



#### Converting JSON link to DataFrame:


```{r}
json_df <- jsonlite::fromJSON(nyt_json_url) 
nyt_json_df <- json_df$results
DT::datatable(nyt_json_df, filter="top")
```


#### Using the class() function confirm it is a DataFrame:

```{r}
class(nyt_json_df)
```

#### Checking column names

```{r}
colnames(nyt_json_df)
```

#### Selecting and Renaming Columns


```{r}
new_nyt_json_df <- nyt_json_df %>%
  select("published_date", "section", "subsection", "byline", "title", "abstract") %>%
  rename("text" = "abstract") %>%
  arrange(desc(published_date))
DT::datatable(new_nyt_json_df, filter="top")
```





#### Count of which section had most viewed articles in the last 30 days

```{r}
new_nyt_json_df2 <- new_nyt_json_df %>%
  group_by(section) %>%
  summarise(count=n()) %>%
  arrange(desc(count))
new_nyt_json_df2
```


```{r}
ggplot(new_nyt_json_df2, aes(x=reorder(section, -count), count)) +
  geom_bar(stat="identity", position="dodge")
```



Articles in the U.S. section were the most viewed on The New York Times website in the past 30 days.  


